### 2013-10-24 src2/thesis.tex
update

\begin{small}
\begin{verbatim} 
__global__ void kernel(int32_t *i1, int32_t *i2, int32_t *r) {

  r[threadIdx.x] = i1[threadIdx.x] + i2[threadIdx.x];

} 
\end{verbatim}
\end{small}

This kernel takes two input arrays, {\tt i1} and {\tt i2}, and computes 
elementwise sums into the result array, {\tt r}. {\tt threadIdx} identifies 
a thread within a block. There is also a {\tt blockIdx} variable that identifies 
the block a thread belongs to but that is not used in this case.

@@

\begin{small}
\begin{verbatim} 
int main(void) {

@@

  return 0;
}
\end{verbatim} 
\end{small}

@@

\begin{small}
\begin{verbatim}
name<<<#Blocks, #Threads/Block, #BytesShared>>>(arg1,..,argN);
\end{verbatim}
\end{small}

In this case one block of 32 threads using no shared memory, is launched.

>>>>

\begin{small}
\begin{Verbatim}[samepage=true]
__global__ void kernel(int32_t *i1, int32_t *i2, int32_t *r) {

  unsigned int gid = blockIdx.x * 
                     blockDim.x + 
                     threadIdx.x;

  r[gid] = i1[gid] + i2[gid];

}

\end{Verbatim}
\end{small}

This kernel takes two input arrays, {\tt i1} and {\tt i2}, and computes 
elementwise sums into the result array, {\tt r}. The {\tt threadIdx} variable identifies 
a thread within a block. There is also a {\tt blockIdx} variable that identifies 
the block a thread and {\tt blockDim.x} specifies the number of threads per block.

@@

\begin{small}
\begin{Verbatim}[samepage=true]
int main(void) {

@@

  return 0;
}
\end{Verbatim} 
\end{small}

@@

\begin{small}
\begin{Verbatim}[samepage=true]
name<<<Blocks, Threads/Block, BytesShared>>>(arg1,..,argN);
\end{Verbatim}
\end{small}

\noindent In this example above one block of 32 threads using no shared memory, is launched.

A kernel that uses shared memory takes a form similar to whats shown below.

\begin{small}
\begin{Verbatim}[samepage=true]
__global__ void kernel2(int32_t *i, int32_t *r) {

  extern __shared__ int32_t sm[];

  unsigned int tid = threadIdx.x; 
  unsigned int gid = blockIdx.x * 
                     blockDim.x + 
                     threadIdx.x;

  sm[tid] = i[gid]; 
  __syncthreads();

  /* Compute on sm */

  __syncthreads();
  r[gid] = sm[tid];

}
\end{Verbatim} 
\end{small}

\noindent A portion of the input array is stored into shared memory. A 
barrier synchronisation is used to ensure that all threads within the block 
has stored its value into shared memory (only necessary if threads will 
communicate across warp boundaries). After computing on the data locally 
it is written back into global memory.
